### 2016-10-28 thesis/intro/intro.tex
tmp commit

\noindent
The second factor to consider is the behavioural changes led by the urbanisation of the population.

\textit{(Expand on this -- physical activity, sociocultural norm, etc.)}
\citep{Malik2013}\\

\noindent
The third factor is the income and socioeconomic status of the countries.
\textit{(Expand on this -- rise in income, availability of health care, etc.)}
\citep{Malik2013}\\

>>>>

\noindent
The second factor to consider is the behavioural changes led by the urbanisation of the population.
Urbanisation is defined as the gradual increase in the proportion of people living in urban areas.
As more people take up urban lifestyle, they are exposed to the new environment where there is a better range of food selection, as well as technological and mechanical advancement in transport and other daily chores that may not be available in rural areas where these people come from.

Although there are many advantages involved with urbanisation, such as access to developed health care systems, education and advanced technologies, the lifestyle change also impose negative health behaviour that ultimately lead to positive energy balance and therefore obesity \citep{Malik2013}.

One of the obvious factors that is linked to urbanisation is the lack of physical activity.
Currently, the recommended amount of physical activity to keep an individual fit and healthy is $\geq$ 150 min of moderate-intensity aerobic physical activity per week, or $\geq$ 30 min of physical activity on most days of the week \citep{Pate1995, WHO2010}.

sociocultural norm

\citep{Malik2013}\\

\noindent
The third factor is the income and socioeconomic status of the countries.
As mentioned briefly in the previous point, access to developed health care system will allow weight maintenance of the population, but most likely be of most benefit for the high-income group.
\textit{(Expand on this -- rise in income, availability of health care, etc.)}
\citep{Malik2013}\\
